# Update Annual Reports

## read in needed scripts
```{r}
source(here::here('admin', 'setup_scripts', '00_global_scripts', '02_render.R'))
source(here::here('admin', 'setup_scripts', '00_global_scripts', '01_general_copy.R'))
targets::tar_make()
```

## set report year
```{r}
# set report year
report_year <- 2024
```

## create pdfs

### all reports (run as-is)
```{r}
render_pdfs(report_year = report_year)
```

### specific reports (type name(s) in between `c()`)
options are 'benthic', 'phyto', 'zoop', 'dwq', 'cwq'
```{r}
render_report(sections = c('dwq'),
              report_type = 'pdfs',
              report_year = report_year)
```

## preview website locally

### all reports (run as-is)
```{r}
render_website(report_year = report_year)
```

### specific reports (type name(s) in between `c()`)
options are 'benthic', 'phyto', 'zoop', 'dwq', 'cwq'
```{r}
render_report(sections = c('dwq'),
              report_type = 'website',
              report_year = report_year)
```

## deploy to website
Once everything looks good, push your changes to `main`, then go to
**Actions > "Deploy Full Site" > Run workflow**. This renders the site
and pushes it live.

The golden mussel page updates automatically; no manual step needed.