# Update Annual Reports

## read in scripts
```{r}
source(here::here('admin', 'setup_scripts', '00_global_scripts', '02_render.R'))
```

## set report year
```{r}
# set report year
report_year <- 2024
```

## generate figures
```{r}
# create_figs(group = c('benthic'))
```

## create pdfs

### all reports (run as-is)
```{r}
quarto::quarto_render(
  profile = 'pdfs'
)
```

### specific reports (type name in between `c()`)
options are 'benthic', 'phyto', 'zoop', 'dwq', 'cwq'
```{r}
render_report(programs = c('zoop'),
              report_type = 'pdfs',
              report_year = report_year)
```

## preview website locally

### all reports (run as-is)
```{r}
render_website(report_year = report_year)
```

### specific reports (type name in between `c()`)
options are 'benthic', 'phyto', 'zoop', 'dwq', 'cwq'
```{r}
render_report(programs = c('benthic'),
              report_type = 'website',
              report_year = report_year)
```

## deploy to website
Once everything looks good, push your changes to `main`, then go to
**Actions > "Deploy Full Site" > Run workflow**. This renders the site
and pushes it live.

The golden mussel page updates automatically; no manual step needed.