# Generate Draft Benthic Report

Code to generate draft versions of the Benthic Annual Report and related website sections.

Press "run" once you've looked over the "Relevant Variables" section to generate draft report.

## Output

Look in the "draft-website-files" folder. All files named "00-<RMD FILE NAME>.html" will open the draft website version.

Right-click and select "view in web browser" to see.

## Relevant Variables

Edit these variables as you choose.

```{r message = FALSE, warning = FALSE}
# Do you want to generate a new Excel sheet and/or plots?
generate_new_excel <- TRUE # TRUE/FALSE
```

------------------------------------------------------------------------

# Code Starts Here ([**DO NOT TOUCH**]{.underline})

```{r results = 'hide', message = FALSE, warning = FALSE}
file_sources <- list.files(path = c('admin/setup_scripts/00_global_scripts','admin/setup_scripts/01_benthic_scripts'), pattern = '.R$', full.names=TRUE, recursive = TRUE)
sapply(file_sources, source, .GlobalEnv)

if(generate_new_excel){
  func_benthic_excel()
}

bookdown::render_book(
  input = 'admin/config-yaml.Rmd',
  output_dir = './sections/benthic/draft-website-files',
  config_file = 'admin/individ-config-files/_benthic-bookdown.yml',
  output_format = 'bookdown::gitbook'
)
```
