# Update Annual Reports

## read in functions (run this first)
```{r}
source(here::here('admin/import_scripts.R'))
```

## generate figures
```{r}
create_figs(group = c('benthic'))
```

## create pdfs

### all reports (run as-is)
```{r}
quarto::quarto_render(
  profile = 'pdfs'
)
```

### specific reports (type name in between `c()`)
options are 'benthic', 'phyto', 'zoop', 'dwq', 'cwq'
```{r}
render_report(programs = c('zoop'),
              report_type = 'pdfs')
```

## preview website locally

### all reports (run as-is)
```{r}
quarto::quarto_render(
  input = 'qmd-files/website',
  as_job = TRUE
)
```

### specific reports (type name in between `c()`)
options are 'benthic', 'phyto', 'zoop', 'dwq', 'cwq'
```{r}
render_report(programs = c('dwq'),
              report_type = 'website',
              report_year = 2024)
```

## deploy to website
Once everything looks good, push your changes to `main`, then go to
**Actions > "Deploy Full Site" > Run workflow**. This renders the site
and pushes it live.

The golden mussel page updates automatically; no manual step needed.